Project Uccle

### 2020-06-09 project.mems.Rmd
cleanup some labels

for (model in to_test) {
  # model <- c(4,1,2,0,1,0)
  fit.name <- paste0("fit", paste0(model, collapse = ""))
  forecast.name <- paste0("forecast", paste0(model, collapse = ""))
  cat("SARIMA(", paste0(model[1:3], collapse = ","), ")(", paste0(model[4:6], collapse = ","), ")[", frequency(seis.h.train), "]", sep = "")
  if (!(fit.name %in% names(models))) {
    cat(" fitting...")
    models[[fit.name]] <- Arima(seis.h.train, model[1:3], model[4:6], lambda=train.bc.lambda)
    cat("DONE")
  }
  if (!(forecast.name %in% names(models))) {
    cat(" forecasting...")
    models[[forecast.name]] <- forecast(models[[fit.name]], h=168*18, lambda=train.bc.lambda)
    cat("DONE")
  }
  cat("\n")
  plotting.model <- models[[fit.name]]
  plotting.forecast <- models[[forecast.name]]
  print(plotting.model)
  print(autoplot(plotting.model) + labs(subtitle = plotting.forecast$method))
  checkresiduals(plotting.model)
  residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
  print(plot_grid(
    autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
    residuals.acf,
    autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
    residuals.pacf,
    nrow = 2
  ))
  print(plot_forecast(plotting.forecast) + autolayer(seis.h.test, series="Original") + ylab("Mean hourly movement (nm)"))
  plots <- show_overlap_and_diff(
    seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
    base.desc = "training set",
    compare.desc = paste0("refit with ", plotting.forecast$method),
    overlap.ylab = "Mean hourly movement (nm)",
    diff.title = "Difference between ts",
    diff.ylab = "nm", diff.ylab.sec="%",
    diff.ylab.sec.accuracy = .01
  )
  print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

@@

  plots <- show_overlap_and_diff(
    seis.h.test, plotting.forecast$mean, xlab=seasonality.xlab,
    base.desc = "test set",
    compare.desc = paste0("forecast with ", plotting.forecast$method),
    overlap.ylab = "Mean hourly movement (nm)",
    diff.title = "Difference between ts",
    diff.ylab = "nm", diff.ylab.sec="%",
    diff.ylab.sec.accuracy = .01
  )
  print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

@@

plot_forecast(plotting.forecast) + 
  autolayer(seis.h.test, series="Test") + 
  autolayer(seis.h.train, series="Train")
plots <- show_overlap_and_diff(
  seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "train series",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
plots <- show_overlap_and_diff(
  seis.h.test[1:length(plotting.forecast$mean)], plotting.forecast$mean, xlab=seasonality.xlab,
  base.desc = "test series",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
accuracy(plotting.forecast, seis.h.test)

@@

plot_forecast(plotting.forecast) + 
  autolayer(seis.h.test, series="Test") + 
  autolayer(seis.h.train, series="Train")
plots <- show_overlap_and_diff(
  seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "train series",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
plots <- show_overlap_and_diff(
  seis.h.test[1:length(plotting.forecast$mean)], plotting.forecast$mean, xlab=seasonality.xlab,
  base.desc = "test series",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
accuracy(plotting.forecast, seis.h.test)

>>>>

for (model in to_test) {
  # model <- c(4,1,2,0,1,0)
  fit.name <- paste0("fit", paste0(model, collapse = ""))
  forecast.name <- paste0("forecast", paste0(model, collapse = ""))
  cat("SARIMA(", paste0(model[1:3], collapse = ","), ")(", paste0(model[4:6], collapse = ","), ")[", frequency(seis.h.train), "]", sep = "")
  if (!(fit.name %in% names(models))) {
    cat(" fitting...")
    models[[fit.name]] <- Arima(seis.h.train, model[1:3], model[4:6], lambda=train.bc.lambda)
    cat("DONE")
  }
  if (!(forecast.name %in% names(models))) {
    cat(" forecasting...")
    models[[forecast.name]] <- forecast(models[[fit.name]], h=168*18, lambda=train.bc.lambda)
    cat("DONE")
  }
  cat("\n")
  plotting.model <- models[[fit.name]]
  plotting.forecast <- models[[forecast.name]]
  print(plotting.model)
  print(autoplot(plotting.model) + labs(subtitle = plotting.forecast$method))
  checkresiduals(plotting.model)
  residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
  print(plot_grid(
    autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
    residuals.acf,
    autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
    residuals.pacf,
    nrow = 2
  ))
  print(plot_forecast(plotting.forecast) + autolayer(seis.h.test, series="Original") + ylab(data.lab) + xlab(seasonality.xlab))
  plots <- show_overlap_and_diff(
    seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
    base.desc = "training set",
    compare.desc = paste0("refit with ", plotting.forecast$method),
    overlap.ylab = data.lab,
    diff.title = NULL,
    diff.ylab = "nm", diff.ylab.sec="%",
    diff.ylab.sec.accuracy = .01
  )
  print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

@@

  plots <- show_overlap_and_diff(
    seis.h.test, plotting.forecast$mean, xlab=seasonality.xlab,
    base.desc = "test set",
    compare.desc = paste0("forecast with ", plotting.forecast$method),
    overlap.ylab = data.lab,
    diff.title = NULL,
    diff.ylab = "nm", diff.ylab.sec="%",
    diff.ylab.sec.accuracy = .01
  )
  print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

@@

plot_forecast(plotting.forecast) + 
  autolayer(seis.h.test, series="Test") + 
  autolayer(seis.h.train, series="Train")
plots <- show_overlap_and_diff(
  seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "train series",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = data.lab,
  diff.title = NULL,
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
plots <- show_overlap_and_diff(
  seis.h.test[1:length(plotting.forecast$mean)], plotting.forecast$mean, xlab=seasonality.xlab,
  base.desc = "test series",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = data.lab,
  diff.title = NULL,
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
accuracy(plotting.forecast, seis.h.test)

@@

plot_forecast(plotting.forecast) + 
  autolayer(seis.h.test, series="Test") + 
  autolayer(seis.h.train, series="Train")
plots <- show_overlap_and_diff(
  seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "train series",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = data.lab,
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
plots <- show_overlap_and_diff(
  seis.h.test[1:length(plotting.forecast$mean)], plotting.forecast$mean, xlab=seasonality.xlab,
  base.desc = "test series",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = data.lab,
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
accuracy(plotting.forecast, seis.h.test)

### 2020-06-09 project.uccs.Rmd
cleanup some labels

for (model in to_test) {
  # model <- c(4,1,2,0,1,0)
  fit.name <- paste0("fit", paste0(model, collapse = ""))
  forecast.name <- paste0("forecast", paste0(model, collapse = ""))
  cat("SARIMA(", paste0(model[1:3], collapse = ","), ")(", paste0(model[4:6], collapse = ","), ")[", frequency(seis.h.train), "]", sep = "")
  if (!(fit.name %in% names(models))) {
    cat(" fitting...")
    models[[fit.name]] <- Arima(seis.h.train, model[1:3], model[4:6])
    cat("DONE")
  }
  if (!(forecast.name %in% names(models))) {
    cat(" forecasting...")
    models[[forecast.name]] <- forecast(models[[fit.name]], h=168*18)
    cat("DONE")
  }
  cat("\n")
  plotting.model <- models[[fit.name]]
  plotting.forecast <- models[[forecast.name]]
  print(plotting.model)
  print(autoplot(plotting.model) + labs(subtitle = plotting.forecast$method))
  checkresiduals(plotting.model)
  residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
  print(plot_grid(
    autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
    residuals.acf,
    autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
    residuals.pacf,
    nrow = 2
  ))
  print(plot_forecast(plotting.forecast) + autolayer(seis.h.test, series="Original") + ylab("Mean hourly movement (nm)"))
  plots <- show_overlap_and_diff(
    seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
    base.desc = "training set",
    compare.desc = paste0("refit with ", plotting.forecast$method),
    overlap.ylab = "Mean hourly movement (nm)",
    diff.title = "Difference between ts",
    diff.ylab = "nm", diff.ylab.sec="%",
    diff.ylab.sec.accuracy = .01
  )
  print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

@@

plot_forecast(plotting.forecast) + 
  autolayer(seis.h.test, series="Original") +
  xlim(52, 70) + ylim(0, 8750)
plot_forecast(plotting.forecast) + 
  autolayer(seis.h.test, series="Original")
plots <- show_overlap_and_diff(
  seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "train series",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
plots <- show_overlap_and_diff(
  seis.h.test[1:length(plotting.forecast$mean)], plotting.forecast$mean, xlab=seasonality.xlab,
  base.desc = "test series",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = "Mean hourly movement (nm)",
  diff.title = "Difference between ts",
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
accuracy(plotting.forecast, seis.h.test)
gg_qqplot(plotting.model[,5])

>>>>

for (model in to_test) {
  # model <- c(4,1,2,0,1,0)
  fit.name <- paste0("fit", paste0(model, collapse = ""))
  forecast.name <- paste0("forecast", paste0(model, collapse = ""))
  cat("SARIMA(", paste0(model[1:3], collapse = ","), ")(", paste0(model[4:6], collapse = ","), ")[", frequency(seis.h.train), "]", sep = "")
  if (!(fit.name %in% names(models))) {
    cat(" fitting...")
    models[[fit.name]] <- Arima(seis.h.train, model[1:3], model[4:6])
    cat("DONE")
  }
  if (!(forecast.name %in% names(models))) {
    cat(" forecasting...")
    models[[forecast.name]] <- forecast(models[[fit.name]], h=168*18)
    cat("DONE")
  }
  cat("\n")
  plotting.model <- models[[fit.name]]
  plotting.forecast <- models[[forecast.name]]
  print(plotting.model)
  print(autoplot(plotting.model) + labs(subtitle = plotting.forecast$method))
  checkresiduals(plotting.model)
  residuals.acf <- autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  residuals.pacf <- autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=168*4)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method))
  print(plot_grid(residuals.acf, residuals.pacf, nrow=2))
  print(plot_grid(
    autoplot(acf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
    residuals.acf,
    autoplot(pacf(plotting.model$residuals, na.action = na.pass, plot=F, lag.max=24)) + scale_x_continuous() + labs(title = paste0("Residuals of ", plotting.forecast$method)),
    residuals.pacf,
    nrow = 2
  ))
  print(plot_forecast(plotting.forecast) + autolayer(seis.h.test, series="Original") + ylab(data.lab) + xlab(seasonality.xlab))
  plots <- show_overlap_and_diff(
    seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
    base.desc = "training set",
    compare.desc = paste0("refit with ", plotting.forecast$method),
    overlap.ylab = data.lab,
    diff.title = NULL,
    diff.ylab = "nm", diff.ylab.sec="%",
    diff.ylab.sec.accuracy = .01
  )
  print(plot_grid(plots[[1]], plots[[2]], nrow = 2))

@@

plot_forecast(plotting.forecast) + 
  autolayer(seis.h.test, series="Original") +
  xlim(52, 70) + ylim(0, 8750)
plot_forecast(plotting.forecast) + 
  autolayer(seis.h.test, series="Original")
plots <- show_overlap_and_diff(
  seis.h.train, plotting.forecast$fitted, xlab=seasonality.xlab,
  base.desc = "train series",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = data.lab,
  diff.title = NULL,
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
plots <- show_overlap_and_diff(
  seis.h.test[1:length(plotting.forecast$mean)], plotting.forecast$mean, xlab=seasonality.xlab,
  base.desc = "test series",
  compare.desc = paste0("refit with ", plotting.forecast$method),
  overlap.ylab = data.lab,
  diff.title = NULL,
  diff.ylab = "nm", diff.ylab.sec="% over ts span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
accuracy(plotting.forecast, seis.h.test)
gg_qqplot(plotting.model[,5])
